Exp1 - Opt w_max and {A,phi)

### 2018-03-16 voltagebudget/analysis/paper_figures.Rmd
In paper figures, now norming all V_osc terms by V_b. Unitless is good.

# --------------------------------------------------------------------
# Summarize over As 
fig1 %>% 
  group_by(As, freq) %>% 
  summarise(
    delta_spikes = mean(delta_spikes), 
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig2

@@

# Trade-off

```{r, fig.width=2.1, fig.height=1.8}
fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=V_osc*1e3)) +
  geom_point(size=0.05, alpha=.4) +
  scale_color_gradient(low="white", high="red", name=expression(V[o] (mvolt))) +
  labs(x="Error (ms)", y="Variance (ms)") +
  theme_classic() +
  theme(
    legend.position="bottom", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc*1e3, y=errors_pop*1e3)) +
  geom_point(size=0.05, alpha=1, color="black") + 
  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
  lims(y=c(0, 10)) +
  theme_classic() -> p2

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc*1e3, y=variances_pop*1e3)) +
  geom_point(size=0.05, alpha=1, color="black") + 
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
  # lims(y=c(0, 10)) +
  theme_classic() -> p3

fig1 %>% 
  filter(rank == 0, freq == 20) %>% 
  ggplot(aes(x=As*1e9, y=V_osc*1e3)) +
  geom_point(size=0.1, alpha=0.6, color="black") + 
  labs(x="A (namp)", y=expression(V[o] (mvolt))) +
  theme_classic() -> p4

plot_grid <- rbind(
  c(NA, NA, NA, NA, 4, 4,   4),
  c(NA, NA, NA, NA, 4, 4,   4),
  c(1,  1,  1,  1, 2, 2,   2),
  c(1,  1,  1,  1, 2, 2,   2),
  c(1,  1,  1,  1, 3, 3,   3),
  c(1,  1,  1,  1, 3, 3,   3))#,
  # c(1,  1,  1,  NA, NA, NA))
grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid)
```

@@

```{r, fig.width=3, fig.height=3}
max_N <- max(fig1$N)

fig1 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc*1e3, y=variances*1e3)) +
  geom_point(size=0.1, alpha=0.1, color="grey") + 
  theme_classic() +
  geom_line(aes(x=V_osc*1e3, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") -> p1

fig1 %>% 
  filter(freq==20) %>% 
  # filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc*1e3, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=2) +
  geom_line(aes(x=V_osc*1e3, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  scale_x_continuous(breaks=c(0, 4, 8)) +
  scale_y_continuous(breaks=c(8, 12)) +
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p2

fig1 %>% 
  filter(freq==20) %>% 
  # filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 5, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc*1e3, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=1) +
  geom_line(aes(x=V_osc*1e3, y=errors_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  scale_x_continuous(breaks=c(0, 4, 8)) +
  scale_y_continuous(breaks=c(2, 8)) +
  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p3

>>>>

# --------------------------------------------------------------------
# Summarize over As 
fig1 %>% 
  group_by(As, freq) %>% 
  summarise(
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig2

@@

```{r, fig.width=1, fig.height=0.8}
fig1 %>%
  filter(rank == 0, freq == 20) %>%
  ggplot(aes(x=As*1e9, y=V_osc*1e3)) +
  geom_point(size=0.1, alpha=0.6, color="black") +
  labs(x="A (namp)", y=expression(V[o] (mvolt))) +
  theme_classic() 
```
# Trade-off

```{r, fig.width=1.5, fig.height=1.9}
fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors_pop*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=1) + 
  labs(x=expression(V[o]/V[b]), y="Avg. error (ms)") +
  lims(y=c(0, 10)) +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  scale_color_gradient(low="lightgrey", high="red") +
  theme_classic() +
  theme(
    legend.position="none") -> p1

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances_pop*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=1) + 
  labs(x=expression(V[o]/V[b]), y="Pop. variance (ms)") +
  scale_color_gradient(low="lightgrey", high="red") +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  theme_classic() +
  theme(
    legend.position="none") -> p2

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=.6) +
  scale_color_gradient(low="lightgrey", high="red", name=expression(V[o]/V[b])) +
  # scale_color_gradient(low="lightgrey", high="red", name="A (namp)") +
  geom_smooth(color="black", method=lm, alpha=0.2, size=.8, linetype='dotted') +
  labs(x="Avg. error (ms)", y="Pop. variance (ms)") +
  theme_classic() +
  theme(
    legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

# plot_grid <- rbind(
#   c(NA, NA, NA, NA, 4, 4,   4),
#   c(NA, NA, NA, NA, 4, 4,   4),
#   c(1,  1,  1,  1, 2, 2,   2),
#   c(1,  1,  1,  1, 2, 2,   2),
#   c(1,  1,  1,  1, 3, 3,   3),
#   c(1,  1,  1,  1, 3, 3,   3))#,
  # c(1,  1,  1,  NA, NA, NA))

plot_grid <- rbind(
  c(NA),
  c(1, 2),
  c(1, 2),
  c(3, 3),
  c(3, 3),
  c(3, 3))

@@

```{r, fig.width=3.7, fig.height=3.1}
max_N <- max(fig1$N)

fig1 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances*1e3)) +
  geom_point(size=0.1, alpha=0.1, color="grey") + 
  theme_classic() +
  geom_line(aes(x=V_osc/V_b, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") -> p1

fig1 %>% 
  filter(freq==20) %>% 
  # filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=2) +
  geom_line(aes(x=V_osc/V_b, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(8, 12)) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p2

fig1 %>% 
  filter(freq==20) %>% 
  # filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 5, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=1) +
  geom_line(aes(x=V_osc/V_b, y=errors_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(2, 8)) +
  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p3
